Predator summary

### 2023-10-26 reports/01_predators.qmd
figs s1 and s2

tar_load(c("predators_agg", "ant_sf", "effort_sf"), 
         store = here::here("_targets"))
source(here::here("R", "sp.R"))
```

@@

Distribution maps of all species in all years, for supplemental.

```{r}
#| label: pred_map
#| warning: false
#| column: screen
#| out-width: 100%
#| fig-height: 9
#| fig-width: 7.5
#| fig-dpi: 600

pred_sf <- predators_agg %>% 
  filter(!str_starts(species, "U")) %>% 
  mutate(common_name = code_to_common(species)) %>% 
  latlon_to_sf(coords = c("lon_mean", "lat_mean"))

@@

pred_class_df <- as.data.frame(pred_class, xy = TRUE) %>% 
  pivot_longer(-c("x", "y"), 
               names_to = "name", 
               values_to = "count") %>% 
  drop_na(count) %>% 
  mutate(name = map_chr(name, \(n) paste(strwrap(n, 15), collapse = "\n")))

p <- ant_basemap() +
  geom_raster(aes(x, y, fill = count), pred_class_df) +
  geom_sf(data = tar_read("ant_sf", store = here::here("_targets"))) +
  scale_fill_brewer(palette = "RdPu", 
                    na.value = NA, 
                    direction = 1,
                    na.translate = FALSE) +
  scale_x_continuous(breaks = seq(-64, -54, by = 4)) +
  scale_y_continuous(breaks = seq(-64, -59, by = 2)) +
  labs(fill = "Ind nmi^-1") +
  facet_wrap(~ name, ncol = 6) +
  coord_sf(xlim = map_bbox[1:2],
           ylim = map_bbox[3:4],
           crs = ant_proj()) +
  theme(legend.position = "top",
        text = element_text(size = 8))

ggsave("figs/s1.jpg", p, width = 6, height = 8, units = "in", dpi = 600)
```

>>>>

tar_load_everything(store = here::here("_targets"))
source(here::here("R", "sp.R"))
source(here::here("R", "predators.R"))
```

@@

Distribution maps of all species in all years, for supplemental. Organized by mammals and birds

```{r}
pred_sf <- predators_agg %>% 
  filter(!str_starts(species, "U")) %>% 
  mutate(common_name = code_to_common(species)) %>% 
  latlon_to_sf(coords = c("lon_mean", "lat_mean"))

@@

pred_class_df <- as.data.frame(pred_class, xy = TRUE) %>% 
  pivot_longer(-c("x", "y"), 
               names_to = "name", 
               values_to = "count") %>% 
  drop_na(count) %>% 
  mutate(name = map_chr(name, \(n) paste(strwrap(n, 20), collapse = "\n")))

```{r}
#| label: bird_climatologies
#| warning: false
#| column: screen
#| out-width: 100%
#| fig-height: 9
#| fig-width: 6.5
#| fig-dpi: 600

bird_class_df <- pred_class_df %>% 
  semi_join(tibble(name = c(
    "Blue petrel",
    "Antarctic shag",
    "Cape petrel",
    "Kelp gull",
    "Antarctic petrel",
    "Southern giant\npetrel",
    "Adélie penguin",
    "Kerguelen petrel",
    "Gentoo penguin",
    "Antarctic tern",
    "Northern giant\npetrel",
    "Pale-faced\nsheathbill",
    "Chinstrap penguin",
    "Southern fulmar",
    "Antarctic prion",
    "Common diving\npetrel",
    "South polar skua",
    "Snow petrel",
    "Emperor penguin",
    "Black-browed\nalbatross"
  )), by = "name")

p <- ant_basemap() +
  geom_raster(aes(x, y, fill = count), bird_class_df) +
  geom_sf(data = ant_sf) +
  scale_fill_brewer(palette = "RdPu", 
                    na.value = NA, 
                    direction = 1,
                    na.translate = FALSE) +
  scale_x_continuous(breaks = seq(-64, -54, by = 4)) +
  scale_y_continuous(breaks = seq(-64, -59, by = 2)) +
  labs(fill = "Ind nmi^-1") +
  facet_wrap(~ name, ncol = 5) +
  coord_sf(xlim = map_bbox[1:2],
           ylim = map_bbox[3:4],
           crs = ant_proj()) +
  theme(legend.position = "top",
        text = element_text(size = 8))

ggsave(here::here("figs/s1.jpg"), 
       p, 
       width = 6.5, 
       height = 9, 
       units = "in", 
       dpi = 600)

p

```{r}
#| label: mammal_climatologies
#| warning: false
#| column: screen
#| out-width: 100%
#| fig-height: 9
#| fig-width: 6.5
#| fig-dpi: 600

mammal_class_df <- pred_class_df %>% 
  anti_join(bird_class_df, by = "name")

p <- ant_basemap() +
  geom_raster(aes(x, y, fill = count), mammal_class_df) +
  geom_sf(data = ant_sf) +
  scale_fill_brewer(palette = "RdPu", 
                    na.value = NA, 
                    direction = 1,
                    na.translate = FALSE) +
  scale_x_continuous(breaks = seq(-64, -54, by = 4)) +
  scale_y_continuous(breaks = seq(-64, -59, by = 2)) +
  labs(fill = "Ind nmi^-1") +
  facet_wrap(~ name, ncol = 3) +
  coord_sf(xlim = map_bbox[1:2],
           ylim = map_bbox[3:4],
           crs = ant_proj()) +
  theme(legend.position = "top",
        text = element_text(size = 8))

ggsave(here::here("figs/s2.jpg"), 
       p, 
       width = 6.5, 
       height = 9, 
       units = "in", 
       dpi = 600)

p
